A Typed Programmatic Interface to Contracts on the Blockchain

### 2021-01-29 papers/execution-model/model.tex
abstract

\author{}
\institute{}

@@

\begin{document}
\maketitle
\pagestyle{plain}
\begin{abstract}
  Integrating blockchain contracts in software systems requires a
  programmatic interface. We propose a typed interface for this
  purpose and establish some properties of the combined system. A
  prototype of the interface is implemented in OCaml for the Tezos
  blockchain. 
\end{abstract}

>>>>

\author{Doan Thi Thu Ha \and
Peter Thiemann\orcidID{0000-0002-9000-1239}}
\institute{University of Freiburg, Germany\\
\email{\{doanha,thiemann\}@informatik.uni-freiburg.de}
}

@@

\begin{document}
\maketitle
\pagestyle{plain}
\begin{abstract}
  Smart contract applications on the blocking can only reach their full potential if
  they can be integrated with traditional software systems. Invoking
  contracts and observing the state of the blockchain requires a
  programmatic interface. We propose a typed API for this
  purpose and establish some properties of the combined
  system. Specifically, we provide an execution model that
  enables us to prove type-safe interaction between programs and the 
  blockchain. We establish further properties of the model that
  translate into requirements on the API. A prototype of the interface
  is implemented in OCaml for the Tezos blockchain.
\end{abstract}
